Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-08-19 main.tex
Updates from Overleaf

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
% \newcommand{\sbunit}{mag~arcsec$^{-2}$}
\newcommand{\sbunit}{\mathrm{mag\ arcsec}^{-2}}
\newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}
\newcommand{\jiaxuan}[1]{\textcolor{orange}{\textbf{Jiaxuan: #1}}}

\newcommand{\code}[1]{\textbf{\texttt{#1}}}
\newcommand{\sersic}{S\'ersic}
\usepackage{CJKutf8}
\usepackage{bm}
\usepackage{appendix}
\usepackage{amsmath,amssymb}

@@

Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content \citep{vanDokkum2018,vanDokkum2019} to their globular cluster populations (Danieli et al. 2022). A central question related to UDGs is what physical mechanisms are responsible for their formation. Before we can answer this question, it is important to reliably determine in what environment they live.
Past UDG studies focused on rich galaxy groups and clusters \citep[e.g.,][]{Yagi2016,Zaritsky2019}, which provides distance information. Although UDGs are also found in field environments \citep{Prole2019,Tanoglidis2021,Kadowaki2021}, most studies of field UDGs lack distances and thus are statistical in nature. UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see \citealt{Roman2019,Prole2019}). This suggests that environment plays a crucial role in the formation and quenching of UDGs. Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, \citealt{Benavides2021}). It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end. A larger UDG sample, especially in low-density environments, is needed to test these hypotheses.

@@

@@

In this work, we use the circularized effective radius $r_{\rm eff}$, defined as the $r_{\rm eff} = r_{\rm eff, sma} \sqrt{b/a}$, where $r_{\rm eff, sma}$ is the effective radius along the semi-major axis of the aligned elliptical isophotes, and $b/a$ is the axis ratio of the isophotes.

@@

\section{Data} \label{sec:data}
\subsection{Hyper Suprime-Camera data}
The Hyper Suprime-Camera Subaru Strategic Program Survey (\citealt{Aihara2018}; hereafter HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}. The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source). HSC data are processed using \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Large Synoptic Survey Telescope (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.

In this work, we use the \code{Wide} layer data from Public Data Release 2 (PDR2, also known as \code{S18A}) of HSC \citealt{Aihara2018}. It covers $\sim 300\ \rm{deg}^2$ in all five bands, which is 1.5 times larger than the dataset analyzed in \citetalias{Greco2018}. One of the key improvements made in \code{S18A} is the sky background subtraction. Compared with previous data releases, \code{S18A} adopted a full focal plane sky subtraction algorithm to overcome the over-subtraction of local sky background around bright objects \citep{Aihara2018,Li2021}. The unprecedented depth and careful sky subtraction makes \code{S18A} an ideal dataset to search for low surface brightness galaxies.

@@

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA \footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies analogous to the Milky Way. NSA is a catalog of parameters of local galaxies derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the new version of NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. It also includes elliptical Petrosian aperture photometry for galaxies, which is considered to be more reliable than the photometry used in older versions. In this paper, we use the stellar mass derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2}. The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.

\section{LSBG search in HSC S18A}
Given an overview of the steps here. Also read SMUDGES paper and discuss some aspects here.

\subsection{Source Detection}\label{sec:detection}
\citetalias{Greco2018} performed a search for extended LSBGs in the first $\sim 200$ deg$^2$ of HSC survey. We continued the work in \citetalias{Greco2018} and extended the search to HSC \code{S18A} data which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to \code{S16A}. We follow the same philosophy of source detection as in \citetalias{Greco2018}, but make several updates to accommodate \code{S18A} data. Below we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity. We refer interested readers to \citetalias{Greco2018} for more details. Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} is also publically available.

\begin{enumerate}
    \item \textbf{Bright source removal}. Bright sources and their associated LSB lights can mimic objects of interest and obstruct effective detection of LSBGs. In this step, we replace pixels related to bright sources with sky noise. The bright sources and their diffuse lights are detected by applying a high thresholding and a low thresholding to the image. A diffuse light component is associated with a bright source if more than 15\% of its pixels are above the high threshold. In this way, we generate a footprint of bright sources in the image.

    Since the sky subtraction in \code{S18A} is significantly better than in previous data releases, LSB features are well conserved after subtracting the sky. Therefore, it makes more sense to set the thresholding based on surface brightness, instead of a certain sigma value above sky background (as in \citetalias{Greco2018}). We set the high threshold to $\mu_{\rm high} = 22\ \mathrm{mag\ arcsec^{-2}}$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \mathrm{mag\ arcsec^{-2}}$ to capture associated diffuse lights.

    %Unlike in \citetalias{Greco2018}, we do not smooth the image prior to thresholding. 
    After this step, there are still a number of small low surface brightness objects, which are typically marginally resolved galaxies or just pixels with high noise fluctuations. We detect and remove them since our main goal is to detect extended LSBGs. We run \code{sep}\footnote{\url{https://sep.readthedocs.io/en/v1.1.x/}} \citep{Barbary2016} on the image cleaned as above. Based on the segmantation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$. This step reduces the number of blended sources. These values ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error. We also get feedbacks from the completeness tests. Not smoothing the images gives us marginal improvement on completeness.

    In the end, we replace pixels within the bright source footprint and small source mask with sky noise. The detection is done in $i$-band, and we use the same mask for all $gri$-bands. This step effectively cleans out objects and features that hinder the detection of LSBGs.

    \item \textbf{Source Extraction}. We use \code{Source Extractor} \citep{Bertin1996} to detect sources on the ``cleaned'' images produced in the previous step. This step remains largely the same as in \citetalias{Greco2018}. The images are convoled with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast. We take a mesh size of $43\arcsec$ (doubles the size used in \citetalias{Greco2018}) to measure the local bacbkground and detect objects that are 0.7$\sigma$ per pixel above the local sky. We also require the object contains at least 100 contiguous pixels to further remove small compact objects. We perform the detection in $g$-band but require all the sources are also detected in $r$-band to exclude possible artifacts.

    \item \textbf{Initial Sample Selection}. In this step, we take the output catalog from the previous step and remove those objects that are not likely to be LSBGs of interest. To be specific, we require objects have $g$-band half-light radius (measured by Source Extractor) larger than $r_{\rm min} = 2.0\arcsec$. We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$. %These cuts are the same as in \citetalias{Greco2018}. 
    %\textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}

\end{enumerate}
After these steps, we have an intial sample containing 86,002 LSBG candidates. \textbf{Why we obtain more sources per sqr deg compared with G18? Sky?} Among these objects, there are still a lot of false positives, including galaxy outskirts, tidal features, blended compact sources, etc. Therefore, we perform an extra ``deblending'' step to remove false positives.

\subsection{Deblending}\label{sec:deblending}
A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or LSB outskirts of  stars and galaxies. In order to remove these objects from our sample, we perform non-parametric modeling for  each object using \code{scarlet}\footnote{\url{https://pmelchior.github.io/scarlet/}} \citep{Melchior2018}. \code{scarlet} is a deblending and modeling tool designed for multi-band data. It utilizes the color and morphology information to seperate blended sources. In the following, we briefly summarize how \code{scarlet} works, and we refer intersted readers to \citet{Melchior2018} for more details. In \code{scarlet}, each source in the scene $Y_i$ is described by a morphology matrix $S_i$ and a Spectral Energy Distribution (SED) vector $A_i$. The goal of modeling is to minimize the object function $f \propto \frac{1}{2}||\sum Y_i - P(\sum A_i S_i)||_2^{2}$ under certain constraints, where $P$ is the convolution with PSF. The morphology matrix of each source is limited to be within a bounding box. In this section, we assume that all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decreases from their centers to outskirts (monotonoicity constraint). Although not all galaxies satisfy the monotonicity constraint, it still provides an easy, sparse, and robust way to deblend overlapping sources. We refer to this modeling method as the ``vanilla scarlet''.

In vanilla scarlet, objects can be modeled with different types of sources, including point source, single-extended source, multi-extended source, compact-extended source, and flat-sky source. The morphology matrix of point source is simply the normalized PSF. For the single-extended source, the morphology matrix follows positivity and monotonicity constraints. The multi-extended source is a combination of two or more single-extended sources, which makes it possible to model more complex structure and color gradient of galaxies. The compact-extended source is a single-extended source initialized using the morphology matrix of a point-source, which encourages the model to be compact. The flat-sky source has uniform color and morphology across the box.

Vanilla scarlet is ideal to identify and remove the false positives in our intial LSBG sample.

We model LSBG candidates using vanilla scarlet as follows.

Our code \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} is also available on GitHub.

\subsubsection{Peak detection}
We first generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candiate. Then we construct a detection image by taking a weighted average of the images in four separate bands. We take the total inverse variance as the weight for each band. This detection image is considered to be deeper than any single band image.

Next, we detect peaks on the detection image. We first run \code{sep} on the detection image using a detection threshold of 4$\sigma$, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels. This step idenfities relatively extended sources in the detection image. However, there are still faint and compact peaks not detected. Therefore, we apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components. Another round of \code{sep} is then ran on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels. This step detects many compact sources that are not detected in the previous step. In the end, we combine the two detection catalogs together.

\subsubsection{Model initialization and optimization}
The deblending step is designed to deblend sources in the vicinity of the target object. The scene will contain both the target object and all the sources in its vicinity. Therefore, the sources being modeled is determined by how extended the target is. We estimate a bounding box based on the detection image, and include all the peaks inside this box to be modeled.

We use a multi-extended source with two components to model the target object, such that it is capable to capture the details of galaxy structure and color. The source is initialized as follows. We start by convolving the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}. After smoothing, the low surface brightness outskirts of target galaxy will become more prominent, which helps intializing the morphology matrix. The smoothed detection image is thresholded using $0.1\sigma$ to remove sky noise, then the morphology matrix $S_i$ of the intial model is determined by constructing a symmetric and monotonic approximation to the region in the detection image around the peak of the target object. The intial SED vector $A_i$ is set to be the color of the image averaged with the spatial weight function $S_i$. As a byproduct of intialization, we get a bounding box which represents the extent of the target object. We also add a flat-sky source to model the local sky around the target. This is helpful for situations where an object overlaps with the LSB outskirts of a bright galaxy.

Then we initialize all the sources inside the bounding box of the target. The extended objects detected in the first detection step are modeled as single-extended sources. For compact objects that are only detected in the second step, we model them as point sources if their FWHM $<$ 5 pixels, otherwise as compact-extended sources. The morphology matrices and SED vectors of these sources are also intialized in the same way as above.

As mentinoed above, we only model sources within the bounding box of the target. However, scattered lights from nearby bright stars and galaxies could bias the modeling within the bounding box. We match our field with the Gaia catalog and mask out stars outside of the bounding box. Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.

As a result of such initialization, we only optimize the object function $f$ defined for sources within the bounding box of the target object. The optimization process uses the adaptive proximal gradient method \citep{Melchior2019}, which is a robust method for optimization with constraints. The model is considered to be converged when the relative changes of parameters are smaller than \code{e\_rel\,=\,2e-4}. Typically convergence is achieved after $\sim 50$ steps of opimization and the whole modeling takes about 40s for each LSBG.

\textbf{For bright sources? Cookie cutter effect}

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
	}
	\caption{An example of the deblending step.}
	\label{fig:vanilla_scarlet_demo}
\end{figure*}

>>>>

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
% \newcommand{\sbunit}{mag~arcsec$^{-2}$}
\newcommand{\sbunit}{\mathrm{mag\ arcsec}^{-2}}
\newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}
\newcommand{\sbeffr}{\overline{\mu}_{\mathrm{eff}}(r)}
\newcommand{\jiaxuan}[1]{\textcolor{orange}{\textbf{Jiaxuan: #1}}}

% \newcommand{\code}[1]{\textbf{\texttt{#1}}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\sersic}{S\'ersic}
\usepackage{CJKutf8}
\usepackage{bm}
\usepackage{appendix}
\usepackage{amsmath,amssymb}

@@

\jiaxuan{Just copied the intro in the Magellan proposal. Not in shape at all.}
Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content \citep{vanDokkum2018,vanDokkum2019} to their globular cluster populations (Danieli et al. 2022). A central question related to UDGs is what physical mechanisms are responsible for their formation. Before we can answer this question, it is important to reliably determine in what environment they live.
Past UDG studies focused on rich galaxy groups and clusters \citep[e.g.,][]{Yagi2016,Zaritsky2019}, which provides distance information. Although UDGs are also found in field environments \citep{Prole2019,Tanoglidis2021,Kadowaki2021}, most studies of field UDGs lack distances and thus are statistical in nature. UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see \citealt{Roman2019,Prole2019}). This suggests that environment plays a crucial role in the formation and quenching of UDGs. Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, \citealt{Benavides2021}). It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end. A larger UDG sample, especially in low-density environments, is needed to test these hypotheses.

@@

The goal of this work is to posit UDGs in the framework of satellite systems of MW analogs. We compare the statistical properties of UDGs with LV satellites and simulations. Try to figure out whether UDG is a special class of galaxies or they are just a tail of mass-size scatter.

@@

@@

\section{Data} \label{sec:data}
\subsection{Hyper Suprime-Camera data}
The Hyper Suprime-Camera Subaru Strategic Program Survey (\citealt{Aihara2018}; hereafter HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}. The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection). HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Large Synoptic Survey Telescope (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.

In this work, we use the \code{Wide} layer data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey. It covers $\sim 300\ \rm{deg}^2$ in all five bands, being 1.5 times larger than the data set (\code{S16A}) analyzed in \citet{Greco2018}. One of the key improvements made in PDR2 is the sky background subtraction. Compared with previous data releases, PDR2 adopted a full focal plane sky subtraction algorithm to overcome the over-subtraction of the local sky background around bright objects \citep{Aihara2018,Li2021}. The unprecedented depth and careful sky subtraction make PDR2 an ideal data set to study low surface brightness galaxies.

@@

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way, then we match the LSBGs to these MW analogs. The NSA catalog provides various physical properties of galaxies in the nearby universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the newer version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. The new version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions. In this paper, we use the stellar mass derived from elliptical Petrosian photometry using \code{kcorrect v4\_2}. The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.

\jiaxuan{Any other data we should introduce? No?}

\section{LSBG search in HSC PDR2}
Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the PDR2 data, which covers $\sim 1.5$ of the sky area in \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section. For those who do not want to be bothered by technical details, we outline the major steps below:
\begin{enumerate}
    \item Source Detection (Sec. \ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources. Then we applied an initial size and color cut based on the output catalog. 
    \item Deblending (Sec. \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}. We use \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 97\% of false positives.
    \item Modeling (Sec. \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
    \item Completeness and measurement errors (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
\end{enumerate}

\subsection{Source Detection}\label{sec:detection}
\citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs. We continued the work in \citetalias{Greco2018} and extended the search to the HSC PDR2 data which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to previous data releases. We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate PDR2 data. These updates are guided by both our understanding of PDR2 data and the completeness tests using mock galaxies. In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity. We refer the interested readers to \citetalias{Greco2018} for more details. Our source detection pipeline \href{https://github.com/johnnygreco/hugs}{\code{hugs}} and \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} are also open-sourced and available online.

\begin{enumerate}
    \item \textbf{Bright source removal}. Bright sources and their associated LSB lights can mimic objects of interest and obstruct the detection of LSBGs. In this step, we replace pixels related to bright sources and small compact sources with sky noise. The bright sources and their diffuse lights are detected in the $i$-band by applying a high thresholding and a low thresholding to the image, respectively. We associate a diffuse light component to a bright source if more than 15\% of its pixels are above the high threshold. In this way, we generate a footprint of bright sources and their LSB lights. Then for the $gri$-bands, we replace every pixel within this footprint with Gaussian noise, where the noise level is determined by masking out all detected sources in the image.

    In \citetalias{Greco2018}, the thresholds are set based on the noise level of the local sky. Thanks to the global sky subtraction in PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less. Therefore, it makes more sense to set the thresholds based on the characteristic surface brightness instead of a certain sigma value above the sky background. In this work, we set the high threshold to $\mu_{\rm high} = 22\ \sbunit$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \sbunit$ to capture the associated diffuse lights. Unlike in \citetalias{Greco2018}, we find it not necessary to smooth the image prior to the thresholding.

    After this step, there are still a number of small and compact LSB objects, which are typically marginally resolved galaxies, blended sources, or just pixels standing out because of noise fluctuation. We add an extra step to detect and remove them since our main goal is to detect extended LSBGs. We run \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} on the ``cleaned'' image as described above. Based on the segmentation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$, and pixels within this mask are also replaced by sky noise. This step significantly improves the purity of LSBG search. The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by completeness tests (Sec. \ref{sec:completeness}). 
    % This step effectively cleans out objects and features that hinder the detection of LSBGs.

    \item \textbf{Source Extraction}. We use \code{Source Extractor} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise. This step remains largely the same as in \citetalias{Greco2018}. The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}. We take a mesh size of $43\arcsec$ (doubles the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background. We also require the object to contain at least 100 contiguous pixels to further remove small compact objects. We perform the detection in the $g$-band, but require that all sources are also detected in the $r$-band to exclude spurious detection and artifacts.

    \item \textbf{Initial Sample Selection}. In this step, we take the output catalog from \code{Source Extractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors. To be specific, we require objects to have $g$-band half-light radius (measured by \code{Source Extractor}) greater than $r_{\rm min} = 2.0\arcsec$. We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$. This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{Greco2018,Zaritsky2019,Tanoglidis2021}. 
    Compared with \citetalias{Greco2018}, we added a new metric on morphology of sources to further remove false positives. For each source, we compute the ratio of the 2-D autocorrelation function (ACT) within an aperture of 5 pixel and an annulus between 5 pixels and 9 pixels from the center. The ACT characterizes the shape, concentration, and spatial correlation of the source. We remove sources that have high autocorrelation ratios $a_{\rm corr} > 1.85$. This step helps to improve the purity of our sample. \jiaxuan{Jenny and Johnny: can you check if this is meaningful to you?} 
    %\textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}
\end{enumerate}

After these steps, we have an initial sample that contains 86,002 LSBG candidates. We obtain more sources per square degree than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction, and our detection is more inclusive for larger galaxies. Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, blended compact sources, etc. Therefore, we perform an extra ``deblending'' step to further remove false positives.

\subsection{Deblending}\label{sec:deblending}
A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or the LSB outskirts of stars and galaxies. Our initial detection cannot distinguish them from the real LSBGs. In order to identify and remove these objects from our sample, we perform an non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}. \code{Scarlet} is a deblending and modeling tool designed for multi-band imaging data. It utilizes the color and morphology information to separate blended objects. In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018} and the online documentation for more details.

In \code{scarlet}, each source $k$ in the cutout is described by a morphology matrix $S^k_i$ and a Spectral Energy Distribution (SED) vector $A^k_i$, and the multi-band images is $Y_i$, where $i$ denotes different bands. The goal of modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF. The morphology matrix of each source is limited to be within a bounding box. We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources should monotonically decrease from center to outskirt (monotonoicity constraint). Apparently, the monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample, this assumption still holds for most cases and provides an easy, sparse, and robust way to deblend overlapping sources. We refer to this modeling method as the \textit{vanilla scarlet}.

In vanilla scarlet, objects can be modeled with different types of sources, including point source, single-extended source, multi-extended source, compact-extended source, and flat-sky source. The morphology matrix of the point source is simply the normalized PSF. The single-extended source has a morphology matrix following positivity and monotonicity constraints. The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient. The compact-extended source is a single-extended source initialized using the morphology matrix of a point-source, which encourages the model to be compact, but still allows the morphology matrix to be extended. The flat-sky source has uniform color and morphology within the bounding box.

Similar to many other modeling code (e.g., \code{galfit}, \code{imfit}), \code{scarlet} asks for the information of detected peaks to initialize sources. The models are then optimized subject to the constraints. Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude blended objects from our sample. We unfold the details in the following sections.
